The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-04 paper.tex
update

Early attempts \citep{Sarkar2015,Yang2017,Zhang2020}\
to model the symmetric Fermi and eROSITA bubbles (collectively we call the Galactic bubbles)\
assumed that the jet is vertical to the Galactic plane. However,\
observation \citep{Gallimore2006} has proposed that\
there is a lack of preferred orientation of jets with respect to a disc normal.\
A number of galaxies in which the jets are tilted to the disc normal\
(e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
including galaxies in which the jets lie in the plane of the disc (e.g. IC 5063, \citealt{Morganti2015}).

@@

The main purpose of this study is to use three-dimensional\
special relativistic hydrodynamics simulations\
involving CR jet injections from the central SMBH in the Galaxy to investigate\
whether the jet scenario is able to produce symmetric Galactic bubbles that are\
consistent with the observed features, including the shape, the\
flat surface brightness, and the sharp edges.\

>>>>

Early attempts \citep{Sarkar2015,Yang2017,Zhang2020}\
to model the symmetric Fermi and eROSITA bubbles (collectively we call the Galactic bubbles)\
assumed that the jet is vertical to the Galactic plane. However,\
observation \citep{Gallimore2006} has proposed that\
there is a lack of preferred orientation of jets with respect to a disc normal.\
In contrast, a number of galaxies in which the jets are tilted to the disc normal\
(e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
including galaxies in which the jets lie in the plane of the disc (e.g. IC 5063, \citealt{Morganti2015}).

@@

The main purpose of this study is to use three-dimensional\
special relativistic hydrodynamics simulations\
involving CR jet injections from the central SMBH in the Galaxy to investigate\
whether the \textit{inclined} jet scenario is able to produce the \textit{symmetric} Galactic bubbles that are\
consistent with the observed features, including the shape, the\
surface brightness (for eROSITA bubbles), and the spectra (for \textit{Fermi} bubbles).\
